Chile Gaps Time

### 2020-01-18 docs/paper.Rmd
update css

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
# knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
```
